Demanding resources: Converging perceptions of challenge and resource characteristics

### 2023-07-15 SIOP2024/SIOP2024convergence.Rmd
results done

@@

@@

anova$Structural <- rowSums(anova[1:10], na.rm=TRUE)
anova$Physical <- rowSums(anova[11:30], na.rm=TRUE)
anova$Interpersonal <- rowSums(anova[31:43], na.rm=TRUE)
anova$Information <- rowSums(anova[44:48], na.rm=TRUE)
anova$Mental <- rowSums(anova[49:58], na.rm=TRUE)
anova$Output <- rowSums(anova[59:67], na.rm=TRUE)
anova$Interact <- rowSums(anova[68:84], na.rm=TRUE)

@@

@@

Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence. Here we categorized each characteristic by its O\*NET "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics). A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001, $\eta^2_{p}$ = `r round(repmeas$ANOVA[2,9],2)` (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001. The only contrasts not broaching statistical significance via Bonferonni-corrected pairwise t-tests were Work Output vs. Physical Work Conditions (*t* = -2.31), Interpersonal Relationships vs. Mental Processes (*t* = .18), and Information Input vs. Physical Work Conditions (*t* = 1.64). The largest contrasts were Interacting with Others vs. Work Output (*t* = 36.09) and Information Input vs. Interacting with Others (*t* = -34.38) and Mental Processes (*t* = -34.10)

>>>>

#t-tests comparing resource, challenge, and hindrance proportions - sheer number of these things.

#t comparing the sheer counts of resource and hindrance
trechind <- t.test(data22$resource, data22$hindrance, paired = TRUE, alternative = "two.sided")

#t comparing the sheer counts of resource and challenge
trech <- t.test(data22$resource, data22$challenge, paired = TRUE, alternative = "two.sided")

#t comparing the sheer counts of hindrance and challenge
thich <- t.test(data22$hindrance, data22$challenge, paired = TRUE, alternative = "two.sided")

library(lsr)

drech <- cohensD(data22$resource, data22$challenge)
dchhi <- cohensD(data22$hindrance, data22$challenge)
drehi <- cohensD(data22$resource, data22$hindrance)

@@

The t-test between mean number of resources and hindrances suggests that respondents experienced more resources than hindrances, *t*(`r trechind$parameter`), = `r trechind$statistic`, *p* < .001, 95% CI = [`r trechind$conf.int[1]`, `r trechind$conf.int[2]`], *d* = `r drehi`. The t-test between mean number of resources and challenges suggests that respondents did not experience more resources than challenges, *t*(`r trech$parameter`), = `r trech$statistic`, *p* = .198, 95% CI = [`r trech$conf.int[1]`, `r trech$conf.int[2]`], *d* = `r drech`. The t-test between mean number of challenges and hindrances suggests that respondents experienced more challenges than hindrances, *t*(`r thich$parameter`), = `r thich$statistic`, *p* < .001, 95% CI = [`r thich$conf.int[1]`, `r thich$conf.int[2]`], *d* = `r dchhi`.

@@

anova$Structural <- rowMeans(anova[1:10], na.rm=TRUE)
anova$Physical <- rowMeans(anova[11:30], na.rm=TRUE)
anova$Interpersonal <- rowMeans(anova[31:43], na.rm=TRUE)
anova$Information <- rowMeans(anova[44:48], na.rm=TRUE)
anova$Mental <- rowMeans(anova[49:58], na.rm=TRUE)
anova$Output <- rowMeans(anova[59:67], na.rm=TRUE)
anova$Interact <- rowMeans(anova[68:84], na.rm=TRUE)

@@

## 36 former "zeroes" got coded as NA when above scales were changed from rowSums to rowMeans - 7/15/23
analysis$value[analysis$value == "NaN"] <- 0
descr::freq(analysis$value)

@@

Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence. Here we categorized each characteristic by its O\*NET "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics). A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001, $\eta^2_{p}$ = `r round(repmeas$ANOVA[2,9],2)` (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001. The only contrast not broaching statistical significance via Bonferonni-corrected pairwise t-tests was Work Output vs. Structural job characteristics (*t* = -1.10). The largest contrasts were Physical work conditions vs. Structural job characteristics (*t* = 25.14), Interpersonal relationships (*t* = -29.25), Mental processes (*t* = -33.84), and Interacting with others (*t* = -35.60)

### 2023-07-15 SIOP2024/SIOP2024convergence.tex
results done

@@

@@

Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence. Here we categorized each characteristic by its O*NET ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics). A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001, \(\eta^2_{p}\) = 0.35 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001. The only contrast approaching statistical significance via Tukey's HSD specification (\emph{p} = .09) was the contrast between Physical Labor (\emph{M} = 0.49) and Business and Financial Operations (\emph{M} = 0.58). Additionally, a Levene's test for homogeneity of variance was non-significant (Levene's = , \emph{p} = .

>>>>

The t-test between mean number of resources and hindrances suggests that respondents experienced more resources than hindrances, \emph{t}(567), = 32.67, \emph{p} \textless{} .001, 95\% CI = {[}21.55, 24.31{]}, \emph{d} = 1.71. The t-test between mean number of resources and challenges suggests that respondents did not experience more resources than challenges, \emph{t}(567), = 1.29, \emph{p} = .198, 95\% CI = {[}-0.20, 0.96{]}, \emph{d} = 0.03. The t-test between mean number of challenges and hindrances suggests that respondents experienced more challenges than hindrances, \emph{t}(567), = -31.58, \emph{p} \textless{} .001, 95\% CI = {[}-23.95, -21.15{]}, \emph{d} = 1.65.

@@

\includegraphics{SIOP2024convergence_files/figure-latex/anova-1.pdf}

\begin{verbatim}
## analysis$value 
##                    Frequency   Percent
## 0                        546  13.73239
## 0.0526315789473684         1   0.02515
## 0.0555555555555556         1   0.02515
## 0.0588235294117647         3   0.07545
## 0.0625                     1   0.02515
## 0.0666666666666667         4   0.10060
## 0.0714285714285714         2   0.05030
## 0.0769230769230769         7   0.17606
## 0.0833333333333333        14   0.35211
## 0.0909090909090909        15   0.37726
## 0.1                       21   0.52817
## 0.111111111111111         28   0.70423
## 0.125                     38   0.95573
## 0.133333333333333          4   0.10060
## 0.142857142857143         39   0.98089
## 0.15                       1   0.02515
## 0.153846153846154          4   0.10060
## 0.157894736842105          1   0.02515
## 0.166666666666667         41   1.03119
## 0.176470588235294          2   0.05030
## 0.181818181818182          9   0.22636
## 0.1875                     3   0.07545
## 0.2                       94   2.36419
## 0.214285714285714          3   0.07545
## 0.222222222222222         40   1.00604
## 0.230769230769231          2   0.05030
## 0.25                      84   2.11268
## 0.266666666666667          2   0.05030
## 0.272727272727273         13   0.32696
## 0.277777777777778          1   0.02515
## 0.285714285714286         45   1.13179
## 0.294117647058824          2   0.05030
## 0.3                       38   0.95573
## 0.3125                     5   0.12575
## 0.333333333333333        172   4.32596
## 0.352941176470588          1   0.02515
## 0.357142857142857          3   0.07545
## 0.363636363636364         20   0.50302
## 0.375                     40   1.00604
## 0.384615384615385          5   0.12575
## 0.4                      110   2.76660
## 0.411764705882353          5   0.12575
## 0.416666666666667         15   0.37726
## 0.428571428571429         42   1.05634
## 0.4375                     2   0.05030
## 0.444444444444444         48   1.20724
## 0.45                       1   0.02515
## 0.454545454545455         19   0.47787
## 0.461538461538462          4   0.10060
## 0.466666666666667          2   0.05030
## 0.470588235294118          2   0.05030
## 0.5                      298   7.49497
## 0.529411764705882          3   0.07545
## 0.533333333333333          4   0.10060
## 0.538461538461538          6   0.15091
## 0.545454545454545         24   0.60362
## 0.555555555555556         60   1.50905
## 0.5625                     2   0.05030
## 0.571428571428571         41   1.03119
## 0.583333333333333         14   0.35211
## 0.588235294117647          2   0.05030
## 0.6                      117   2.94266
## 0.611111111111111          2   0.05030
## 0.615384615384615          5   0.12575
## 0.625                     59   1.48390
## 0.631578947368421          1   0.02515
## 0.636363636363636         21   0.52817
## 0.642857142857143          4   0.10060
## 0.647058823529412          5   0.12575
## 0.666666666666667        202   5.08048
## 0.6875                     5   0.12575
## 0.692307692307692          7   0.17606
## 0.7                       46   1.15694
## 0.705882352941177          4   0.10060
## 0.714285714285714         38   0.95573
## 0.727272727272727         29   0.72938
## 0.733333333333333          6   0.15091
## 0.75                     159   3.99899
## 0.769230769230769         10   0.25151
## 0.777777777777778         74   1.86117
## 0.785714285714286          8   0.20121
## 0.8                      125   3.14386
## 0.8125                     1   0.02515
## 0.818181818181818         20   0.50302
## 0.823529411764706          3   0.07545
## 0.833333333333333         59   1.48390
## 0.846153846153846          3   0.07545
## 0.857142857142857         38   0.95573
## 0.866666666666667          7   0.17606
## 0.875                     47   1.18209
## 0.882352941176471          8   0.20121
## 0.888888888888889         48   1.20724
## 0.894736842105263          1   0.02515
## 0.9                       50   1.25755
## 0.909090909090909         16   0.40241
## 0.916666666666667         15   0.37726
## 0.923076923076923          4   0.10060
## 0.928571428571429          9   0.22636
## 0.933333333333333          8   0.20121
## 0.9375                     5   0.12575
## 0.941176470588235          8   0.20121
## 1                        640  16.09658
## Total                   3976 100.00000
\end{verbatim}

\begin{verbatim}
## $ANOVA
##        Effect DFn  DFd        SSn      SSd         F             p p<.05
## 1 (Intercept)   1  567 1146.04761 171.5620 3787.6047 3.580669e-253     *
## 2       scale   6 3402   92.90682 182.9607  287.9206 7.175910e-299     *
##         ges
## 1 0.7637413
## 2 0.2076457
## 
## $`Mauchly's Test for Sphericity`
##   Effect         W            p p<.05
## 2  scale 0.4208255 6.425345e-91     *
## 
## $`Sphericity Corrections`
##   Effect       GGe         p[GG] p[GG]<.05       HFe         p[HF] p[HF]<.05
## 2  scale 0.7801204 6.574489e-234         * 0.7874087 4.617424e-236         *
\end{verbatim}

\begin{verbatim}
## 
##  Descriptive statistics by group 
## group: Information
##    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
## X1    1 568 0.62 0.38   0.67    0.65 0.49   0   1     1 -0.46    -1.27 0.02
## ------------------------------------------------------------ 
## group: Interact
##    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
## X1    1 568 0.67 0.27   0.75     0.7 0.26   0   1     1 -0.83    -0.07 0.01
## ------------------------------------------------------------ 
## group: Interpersonal
##    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
## X1    1 568 0.57 0.26    0.6    0.58 0.27   0   1     1 -0.36    -0.61 0.01
## ------------------------------------------------------------ 
## group: Mental
##    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
## X1    1 568 0.71 0.29   0.78    0.75 0.33   0   1     1 -1.01     0.16 0.01
## ------------------------------------------------------------ 
## group: Output
##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
## X1    1 568 0.48 0.37    0.5    0.48 0.49   0   1     1 0.07    -1.36 0.02
## ------------------------------------------------------------ 
## group: Physical
##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
## X1    1 568 0.21 0.24   0.14    0.17 0.21   0   1     1 1.21     0.92 0.01
## ------------------------------------------------------------ 
## group: Structural
##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
## X1    1 568  0.5 0.24    0.5     0.5 0.25   0   1     1 0.04    -0.62 0.01
\end{verbatim}

@@

\begin{quote}
Note. This is all off because the ``scales'' have different numbers of items, so it's not appropriate to use sums as scale scores. Maybe revisit with means.
\end{quote}

Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence. Here we categorized each characteristic by its O*NET ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics). A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001, \(\eta^2_{p}\) = 0.21 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001. The only contrast not broaching statistical significance via Bonferonni-corrected pairwise t-tests was Work Output vs.~Structural job characteristics (\emph{t} = -1.10). The largest contrasts were Physical work conditions vs.~Structural job characteristics (\emph{t} = 25.14), Interpersonal relationships (\emph{t} = -29.25), Mental processes (\emph{t} = -33.84), and Interacting with others (\emph{t} = -35.60)
